Malacology: A Programmable Storage System

### 2016-10-17 paper/paper.tex
staged
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

We wanted to implement CORFU and we had two choices: build it from the ground
up or do it on top of Malacology. To show the feasability of building on
Malacology our evaluation focuses on the performance of the internal
abstractions that support the Malacogy interfaces. First, we benchmark
scenarios where contention is at the sequencer by examining the intefaces used
to map ZLog onto Malacology; specifically, we describe the sequencer
implementation and the propogation logical device interfaces. Next, we
benchmark scenarios when there are multiple logs by using Mantle to (1)
balance sequencers across a cluster and (2) recover from failure.

@@

We evaluate the load balancing interface by showing how the cluster of servers
housing sequencers alleviate load.  The experiments use our internal cluster
which uses 10 nodes to store objects, one node to monitor the cluster, and 3
nodes that can accomodate sequencers. The workload is two logs, one with 7
clients and the other with 8 clients; we chose this workload because this load
is the point at which a single physical server gets overloaded.

>>>>

We wanted to implement CORFU and we had two choices: build it from the ground
up or do it on top of Malacology. To show the feasability of building on
Malacology our evaluation focuses on the performance of the internal
abstractions when used for to construct the Mantle and ZLog services. First, we
benchmark scenarios where contention is at the sequencer by examining the
intefaces used to map ZLog onto Malacology; specifically, we describe the
sequencer implementation and the propogation of object \& data interfaces
interfaces. Next, we benchmark scenarios when there are multiple logs by using
Mantle to (1) balance sequencers across a cluster and (2) recover from failure.

@@

We evaluate the load balancing interface by showing how the cluster of servers
housing sequencers alleviates load.  The experiments are run on a cluster with
10 nodes to store objects, one node to monitor the cluster, and 3 nodes that
can accomodate sequencers. The workload has up to 6 logs each with 2 clients.
Figure~\ref{CITEME} shows the throughput per sequencer when all seqeuencers are
co-located of one physical server. Two sequencers on the same server show no
performance degradation but co-locating 3, 4, 5, or 6 sequencers leads to a
2x, 3x, 4x, and 5x slowdown, respectively. For the rest of the experiments we
load balance 3, 4, 5, or 6 sequencers across the cluxter because this is hte
point at which a single physical server gets overloaded.

Figure~\ref{CITEME} shows the performance profiles of the sequencers as they
migrate around the cluster. Each graph in that figure shows different ``waves"
of sequencers, where a ``wave" is a burst of clients trying to append to the
end of the log. These waves are examples of hotspots and flash crowds; they are
dynamic and resource constrained because clients access a shared resource. Wave
1, policy 1 shows how the sequencers initially get distributed poorly. From x
to x seconds, all seqeuencers are co-located. At x seconds, 3 of the sequencers
(1, 2, 3) migrate off the first server and onto the second one; this is what we
want.
